---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Demonstrating Stock Price Prediction methods to identify the trade across tech firms - Intel, Nvidia, AMD. The data is caputed across 3 years starting from March 2019 to March 2022. The data is extracted from Yahoo Finance.

Columns extracted from Yahoo Finance:

1."Date" : Trading date of a stock
2."Open" : Opening price of a stock as per the day
3."High" : High is a stock's highest trading price of the day
4."Low" : Low is a stock's lowest trading price of the day
5."Close" : Closing price of a stock
6."Adj.Close" : The closing price after adjustments for all applicable splits and dividend distributions.
7."Volume" : Volume measures the number of a stock’s shares that are traded on a stock exchange in a day or a period of time

The data is captured at day level for all the tech firms

####Installing required packages
```{r}
library(prophet)
library(quantmod)
library(forecast)
library(tseries)
library(timeSeries)
library(dplyr)
library(fGarch)
library(xts)
```

```{r}
nvidia <- getSymbols("NVDA", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)
amd <- getSymbols("AMD", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)
intel <- getSymbols("INTC", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)

indf_data1 <- Cl(nvidia)
indf_data2 <- Cl(amd)
indf_data3 <- Cl(intel)

```

Nvidia stock market plot

```{r}
chart_Series(indf_data1, col = "black")
add_SMA(n = 100, on = 1, col = "red")
add_SMA(n = 20, on = 1, col = "black")
add_RSI(n = 14, maType = "SMA")
add_BBands(n = 20, maType = "SMA", sd = 1, on = -1)
add_MACD(fast = 12, slow = 25, signal = 9, maType = "SMA", histogram = TRUE)
```

AMD stock market plot

```{r}
chart_Series(indf_data2, col = "black")
add_SMA(n = 100, on = 1, col = "red")
add_SMA(n = 20, on = 1, col = "black")
add_RSI(n = 14, maType = "SMA")
add_BBands(n = 20, maType = "SMA", sd = 1, on = -1)
add_MACD(fast = 12, slow = 25, signal = 9, maType = "SMA", histogram = TRUE)
```

Intel stock market plot

```{r}
chart_Series(indf_data3, col = "black")
add_SMA(n = 100, on = 1, col = "red")
add_SMA(n = 20, on = 1, col = "black")
add_RSI(n = 14, maType = "SMA")
add_BBands(n = 20, maType = "SMA", sd = 1, on = -1)
add_MACD(fast = 12, slow = 25, signal = 9, maType = "SMA", histogram = TRUE)
```

```{r}
indf_log1 <- log(indf_data1)
indf_log2 <- log(indf_data2)
indf_log3 <- log(indf_data3)
head(indf_log1, n = 2)
tail(indf_log1, n = 2)
head(indf_log2, n = 2)
tail(indf_log2, n = 2)
head(indf_log3, n = 2)
tail(indf_log3, n = 2)
```

```{r}
plot(indf_log1, main = "log Nvidia chart")
plot(indf_log2, main = "log AMD chart")
plot(indf_log3, main = "log Intel chart")
```

```{r}
acf_log1 <- acf(indf_log1, lag.max = 320)
acf_log2 <- acf(indf_log2, lag.max = 320)
acf_log3 <- acf(indf_log3, lag.max = 320)
pacf_log1 <- pacf(indf_log1, lag.max = 320)
pacf_log2 <- pacf(indf_log2, lag.max = 320)
pacf_log3 <- pacf(indf_log3, lag.max = 320)
```

```{r}
indf_diff1 <- diff(indf_log1, lag = 1)
indf_diff1 <- na.locf(indf_diff1, na.rm = TRUE,fromLast = TRUE)
indf_diff2 <- diff(indf_log2, lag = 1)
indf_diff2 <- na.locf(indf_diff2, na.rm = TRUE,fromLast = TRUE)
indf_diff3 <- diff(indf_log3, lag = 1)
indf_diff3 <- na.locf(indf_diff3, na.rm = TRUE,fromLast = TRUE)
plot(indf_diff1)
plot(indf_diff2)
plot(indf_diff3)
```

As the log data is not stationary, we should difference at certain lag for it to be stationary.

Augmented Dickey Fuller Test

```{r}
adf1 <- adf.test(indf_log1, alternative = c("stationary", "explosive"), k = 0)
adf2 <- adf.test(indf_log2, alternative = c("stationary", "explosive"), k = 0)
adf3 <- adf.test(indf_log3, alternative = c("stationary", "explosive"), k = 0)
adf1
adf2
adf3
```

```{r}
library(caTools)
train_data1 <- indf_diff1[1:365]
train_data2 <- indf_diff2[1:365]
train_data3 <- indf_diff3[1:365]

library(forecast)
set.seed(123)
arima_model1 <- auto.arima(train_data1, stationary = TRUE, ic = c("aicc", "aic", "bic"), 
                          trace = TRUE)
arima_model2 <- auto.arima(train_data2, stationary = TRUE, ic = c("aicc", "aic", "bic"), 
                          trace = TRUE)
arima_model3 <- auto.arima(train_data3, stationary = TRUE, ic = c("aicc", "aic", "bic"), 
                          trace = TRUE)

summary(arima_model1)
summary(arima_model2)
summary(arima_model3)
checkresiduals(arima_model1) #diagnostic checking
checkresiduals(arima_model2) #diagnostic checking
checkresiduals(arima_model3) #diagnostic checking
```

```{r}
arima1 <- arima(train_data1, order = c(0, 0, 2))
arima2 <- arima(train_data2, order = c(2, 0, 0))
arima3 <- arima(train_data3, order = c(1, 0, 3))
summary(arima1)
summary(arima2)
summary(arima3)

forecast1 <- forecast(arima1, h = 100)
forecast2 <- forecast(arima2, h = 100)
forecast3 <- forecast(arima3, h = 100)
plot(forecast1)
plot(forecast2)
plot(forecast3)
```


```{r}
forecast_ori1 <- forecast(arima1, h = 200)
a <- ts(indf_log1)
forecast_ori1 %>% autoplot() + autolayer(a)

forecast_ori2 <- forecast(arima2, h = 100)
a <- ts(indf_log2)
forecast_ori2 %>% autoplot() + autolayer(a)

forecast_ori3 <- forecast(arima3, h = 100)
a <- ts(indf_log3)
forecast_ori3 %>% autoplot() + autolayer(a)

```


##Implementing STL Approach for Stock Price Forecasting

```{r}
nvidia <- getSymbols("NVDA", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)
amd <- getSymbols("AMD", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)
intel <- getSymbols("INTC", src="yahoo", from="2019-03-09", to = "2021-03-09",auto.assign = FALSE)

indf_data1 <- Cl(nvidia)
indf_data2 <- Cl(amd)
indf_data3 <- Cl(intel)
```

```{r}
freq <- 7
adj <- ts(indf_data1, frequency = freq)

whole.periods <- floor(nrow(adj) / freq)
partial.periods <- nrow(adj) %% freq

desired.test <- 3
training.end.row <- whole.periods + 1
training.end.col <- ifelse(partial.periods == 0, freq - desired.test, freq - partial.periods - desired.test)
if(partial.periods < desired.test){
  training.end.row <- whole.periods
  training.end.col <- freq - (desired.test - partial.periods)
}
training.ts <- window(adj, c(1,1), c(training.end.row,training.end.col))
testing.ts <- window(adj, c(training.end.row, training.end.col + 1))

fit.stl <- stl(training.ts[,1], s.window = "period")

plot(fit.stl, main="STL Decomposition")


forecasted.adj <- stlf(training.ts[,1], s.window = "period", method="arima", h=desired.test)
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o weekly data)")

accuracy(forecasted.adj, testing.ts)
```
```{r, fig.width=10, fig.height=4}
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o month data)", xlim = c(60, 75))
```

```{r}
freq <- 7
adj <- ts(indf_data2, frequency = freq)

whole.periods <- floor(nrow(adj) / freq)
partial.periods <- nrow(adj) %% freq

desired.test <- 3
training.end.row <- whole.periods + 1
training.end.col <- ifelse(partial.periods == 0, freq - desired.test, freq - partial.periods - desired.test)
if(partial.periods < desired.test){
  training.end.row <- whole.periods
  training.end.col <- freq - (desired.test - partial.periods)
}
training.ts <- window(adj, c(1,1), c(training.end.row,training.end.col))
testing.ts <- window(adj, c(training.end.row, training.end.col + 1))

fit.stl <- stl(training.ts[,1], s.window = "period")

plot(fit.stl, main="STL Decomposition")

forecasted.adj <- stlf(training.ts[,1], s.window = "period", method="arima", h=desired.test)
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o weekly data)")

accuracy(forecasted.adj, testing.ts)
```
```{r, fig.width=10, fig.height=4}
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o month data)", xlim = c(60, 75))
```


```{r}
freq <- 7
adj <- ts(indf_data3, frequency = freq)

whole.periods <- floor(nrow(adj) / freq)
partial.periods <- nrow(adj) %% freq

desired.test <- 3
training.end.row <- whole.periods + 1
training.end.col <- ifelse(partial.periods == 0, freq - desired.test, freq - partial.periods - desired.test)
if(partial.periods < desired.test){
  training.end.row <- whole.periods
  training.end.col <- freq - (desired.test - partial.periods)
}
training.ts <- window(adj, c(1,1), c(training.end.row,training.end.col))
testing.ts <- window(adj, c(training.end.row, training.end.col + 1))

fit.stl <- stl(training.ts[,1], s.window = "period")

plot(fit.stl, main="STL Decomposition")
forecasted.adj <- stlf(training.ts[,1], s.window = "period", method="arima", h=desired.test, lambda = 4)
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o weekly data)")

accuracy(forecasted.adj, testing.ts)
```




```{r, fig.width=10, fig.height=4}
plot(forecasted.adj, main="Forecasts of NWN from STL and ARIMA (w/o month data)", xlim = c(60, 75))
```


